Formal verification of train route planning

### 2025-06-27 paper/main.tex
correction de la composition

The system is then represented by a formula:
\begin{verbatim}
    Spec == Init /\  [][Next]_variables
\end{verbatim}%Revoir la syntaxe au cas où / remplacer par le jolie tla2latex
where variables is the tuple of all variables. The intended meaning is that the initial configuration is specified in \mintinline{C}{Init} and steps follow the \mintinline{C}{Next} formula.  Actually, presently, in our formal semantics, nothing forces a rule to be applied. As a consequence, an ongoing train may never reach its next block. Thanks to TLA+, we can ensure that a rule will eventually be applied (if it can be). Those are known as weak fairness conditions. Again, we specify it as follows. %\todo{WF condition?}

@@

First,  for any train $\tid{i} \in \trains$, we append the orders of the train in $S_k$ to the corresponding ones in $S$. %let $P_0 = S.\Gamma[\tid{i}].P$ and $P_k = S_k.\Gamma[\tid{i}].P$, then set $\Gamma'[\tid{i}] = \Gamma[\tid{i}][ P \leftarrow P_0 \cdot P_k]$. 
Second, we proceed by updates of $E$ and $\sigma$. At first, we set $E' = E$ and $\sigma' = \sigma$. We begin to append to $E'$, for any train, all the handlers within $S_k$.

@@

\subsection{Simplification}

\subsection{Experiments} 
Parler des expériences

>>>>

The system is then represented by a formula:
\begin{verbatim}
    Spec == Init /\ [][Next]_variables /\ WF_variables(Next)
\end{verbatim}%Revoir la syntaxe au cas où / remplacer par le jolie tla2latex
where variables is the tuple of all variables. The intended meaning is that the initial configuration is specified in \mintinline{C}{Init} and steps follow the \mintinline{C}{Next} formula.  Without the weak fairness condition \mintinline{C}{WF_variables(Next)},  nothing forces a rule to be applied. As a consequence, an ongoing train could never reach its next block. The weak fairness condition prevents this incorrect simulation.

@@

First,  for any train $\tid{i} \in \trains$, we append the orders of the train in $S_k$ to the corresponding ones in $S$. %let $P_0 = S.\Gamma[\tid{i}].P$ and $P_k = S_k.\Gamma[\tid{i}].P$, then set $\Gamma'[\tid{i}] = \Gamma[\tid{i}][ P \leftarrow P_0 \cdot P_k]$. 
Second, we proceed by updates of $E$ and $\sigma$. At first, we set $E' = E$ and $\sigma' = \sigma$. We begin to append to $E'$, for any train, all the handlers within $S_k$. To each train $\tid{i}$, we had for its first step (within $X_k$, seen within the composition): an $\auth$ order in $E'[\tid]$.

@@

\paragraph{Optimisations. } We apply some optimisations on the orders. For instance, we remove orders that do not alternate: $\su{d}{\vec{b}} \cdot \su{d}{\vec{b}} \cdot P$ by $\su{d}{\vec{b} \cdot \vec{b'}} \cdot P$. In the same way,  we remove empty lists, singleton lists: if $Len(\vec{b}) \leq 1$, we replace $\su{d}{\vec{b}} \cdot P$ by $P$. We have few more heuristics that we do not show here due to lack of space.

\paragraph{Experiments}  Parler des expériences
